Tests of measurement invariance via stochastic processes: {S}ome properties

### 2013-08-12 frontiers/frontiers.Rnw
update figure part, change code to include R code naturally
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@236 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\readme{Ting: The problem with the last statistic is having
  fplot=TRUE.  To get around this, you can add random noise or set
  fplot=FALSE (I've done the latter).}
<<Get Estimate Alternative Way>>=
DM<-sctest(theta, as.numeric(yg$agegroup), parm=1:4, stat="DM", fplot=TRUE) 
DM
CvM<-sctest(theta, as.numeric(yg$agegroup), parm=1:4, stat="CvM", fplot=TRUE) 
CvM
maxLM<-sctest(theta, as.numeric(yg$agegroup), parm=1:4, stat="maxLM", fplot=FALSE) 
maxLM
@

\begin{figure}
\label{fig:statistics}
\includegraphics[page=1]{Rplots}
\end{figure}

\begin{figure}
\label{fig:statistics}
\includegraphics[page=2]{Rplots}
\end{figure}

@@

<<Get Estimate Alternative Way for Ordinal>>=
WDMo<-sctest(theta, as.numeric(yg$agegroup),parm=1:4, stat="WDMo", fplot=TRUE)
WDMo 
maxLMo<-sctest(theta, as.numeric(yg$agegroup),parm=1:4, stat="maxLMo", 
               fnl=opval1, fplot=TRUE)
maxLMo
@

\begin{figure}
\label{fig:statistics}
\includegraphics[page=3]{Rplots}
\end{figure}

\begin{figure}
\label{fig:statistics}
\includegraphics[page=4]{Rplots}
\end{figure}

@@

In Simulation 1, we examined the extent to which the proposed tests
are sensitive to the specific model parameter that violates measurement
invariance.  If, say, a factor loading violates measurement
invariance, it is plausible that this violation impacts other
parameters such as factor covariances or other loadings 
associated with the factor in question.  Thus, the goal of the
simulation was to examine the extent to which the proposed tests
attribute the measurement invariance violation to the parameters that
are truly in violation.

>>>>

\begin{figure}
\caption{Get Continuous Estimate DM Alternative Way}
\label{fig:conti1res}
\setkeys{Gin}{width=\textwidth}
<<conti1res, fig=TRUE, height=7, width=7>>=
DM<-sctest(theta, as.numeric(yg$agegroup), parm=1:4, stat="DM", fplot=TRUE) 
DM
@
\end{figure}

\begin{figure}
\caption{Get Continuous Estimate CvM Alternative Way}
\label{fig:conti2res}
\setkeys{Gin}{width=\textwidth}
<<conti2res, fig=TRUE, height=7, width=7>>=
CvM<-sctest(theta, as.numeric(yg$agegroup), parm=1:4, stat="CvM", fplot=TRUE) 
CvM
@
\end{figure}

<<conti3resmaxLM>>=
maxLM<-sctest(theta, as.numeric(yg$agegroup), parm=1:4, stat="maxLM", fplot=FALSE) 
maxLM
@

@@

\begin{figure}
\caption{Get Ordinal Estimate WDMo Alternative Way}
\label{fig:ord1res}
\setkeys{Gin}{width=\textwidth}
<<ord1res, fig=TRUE, height=7, width=7>>=
WDMo<-sctest(theta, as.numeric(yg$agegroup),parm=1:4, stat="WDMo", fplot=TRUE)
WDMo 
@
\end{figure}

\begin{figure}
\caption{Get Ordinal Estimate maxLMo Alternative Way}
\label{fig:ord2res}
\setkeys{Gin}{width=\textwidth}
<<ord2res, fig=TRUE, height=7, width=7>>=
maxLMo<-sctest(theta, as.numeric(yg$agegroup),parm=1:4, stat="maxLMo", 
               fnl=opval1, fplot=TRUE)
maxLMo 
@
\end{figure}

@@

In Simulation 1, we examined the extent

 to which the proposed tests
are sensitive to the specific model parameter that violates measurement
invariance.  If, say, a factor loading violates measurement
invariance, it is plausible that this violation impacts other
parameters such as factor covariances or other loadings 
associated with the factor in question.  Thus, the goal of the
simulation was to examine the extent to which the proposed tests
attribute the measurement invariance violation to the parameters that
are truly in violation.
